### 2020-04-30 serial.tex
ok

Using cohort-based approaches, we define forward and backward serial intervals.
The forward serial-interval distribution describes the renewal process between symptomatic cases, and therefore, its initial distribution provides the correct link between $r$ and \RR.
While our results support the use of serial interval distributions for calculating \RR, 
they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
In particular, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial interval data for accurate estimation of time-varying reproduction numbers;
however, our study demonstrates that early serial interval data is required to estimate \RR and using up-to-date serial interval data can, in fact, underestaimte \RR.
Moreover, \cite{tempvar} recently analyzed case reports of COVID-19 from over 30 countries to estimate their time-varying reproduction numbers but relied on a serial-interval distribution;
given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the initial forward serial interval distributions is likely to vary across different countries.

Future studies should aim to characterize spatiotemporal variation in serial intervals and understand the drivers of their differences.

@@

Despite these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
To our knowledge, most, if not all, existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \Ro, of the COVID-19 pandemic.

>>>>

Using cohort-based approaches, we define forward and backward serial intervals.
The forward serial-interval distribution describes the renewal process between symptomatic cases, and therefore, its initial distribution provides the correct link between $r$ and \RR.
While our results support the use of serial interval distributions for calculating \RR, 
they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
In particular, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial interval data for accurate estimation of time-varying reproduction numbers;
however, our study demonstrates that early serial interval data is required to estimate \RR and using up-to-date serial interval data can, in fact, underestaimte \RR.
Moreover, \cite{tempvar} recently analyzed case reports of COVID-19 from over 30 countries to estimate their time-varying reproduction numbers but relied on a serial-interval distribution;
given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the initial forward serial interval distributions is likely to vary across different countries.
We suggest that modelers should aim to characterize spatiotemporal variation in initial forward serial-interval distributions and understand their changes over time.
These modeling approaches should be necessarily coupled with intensive epidemiological investigation through contact tracing at the very beginning of the outbreak in order to characterize the initial forward serial-interval distribution, particularly for an emerging epidemic such as COVID-19.

@@

Despite these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
To our knowledge, most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \Ro, of the COVID-19 pandemic.
